Connecting the Popularity Adjusted Block Model to the Generalized Random Dot Product Graph for Clustering and Parameter Estimation

### 2020-09-23 summary.Rmd
fixed citation for pabm

## The popularity adjusted block model (PABM) \cite{noroozi2019estimation} and the generalized random dot product graph \cite{rubindelanchy2017statistical}

>>>>

## The popularity adjusted block model (PABM) \cite{307cbeb9b1be48299388437423d94bf1} and the generalized random dot product graph \cite{rubindelanchy2017statistical}
